\documentclass[11pt,letterpaper]{article}
\usepackage{changepage}
\usepackage[T1]{fontenc}
\usepackage[margin=1.25cm]{geometry}
\usepackage[pdftitle={Logan Chadderdon - Resume},%
pdfauthor={Logan Chadderdon}, pdfcreator={LaTeX}, pdfproducer={pdfTeX},%
pdfsubject={Logan Chadderdon, Software Developer, Resume},%
pdfkeywords={programming software development application web mobile}]{hyperref}
\usepackage[none]{hyphenat}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{mdwlist}
\usepackage[letterspace=125]{microtype}
\usepackage{multicol}
\usepackage[parfill]{parskip}
\usepackage{tabularx}

\pagestyle{empty}
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}
\newcommand{\CS}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf \#}}

\setcounter{secnumdepth}{-1}
\newcommand{\Hsep}{\vspace{4mm} \hrule \vspace{-1mm}}


\begin{document}

\begin{minipage}{\textwidth}

\begin{center}
\LARGE \bfseries Logan W. Chadderdon
\end{center}

8185 E. Crooked Tree Trail \hfill (520) 344-0470

\vspace{-3mm}
\begin{multicols}{3}
Tucson, AZ 85715 

\begin{center}
\href{http://lwchadderdon.com}{lwchadderdon.com}
\end{center}

\hfill \href{mailto:LWChadderdon@gmail.com}{LWChadderdon@gmail.com}

\end{multicols}


\vspace{-1mm}
\hrule

% \section{\scshape Career Objective}
% \vspace{-2mm}
% I am seeking a career in computer programming.
% Many avenues of software development interest me, including video game design and applications for the web, mobile, and desktop platforms.
% \Hsep

\section{\scshape Education}
\vspace{-2mm}
{\bfseries University of Arizona} - Tucson, AZ \hfill B.S. Computer Science

GPA 3.62 \hfill May 2014

\Hsep

\section{\scshape Coursework}
\vspace{-3mm}
Completing large and complex projects, such as a blog or implementing dynamic memory management,
has helped me learn how to quickly write efficient and maintainable code.
\vspace{2mm}
\begin{itemize}
 \item Languages: {\bfseries Python}, Java, C, SQL, Haskell, Prolog, MatLab, VBA
 \item Web: HTML, CSS, JavaScript, PHP, JSP, Oracle, MySQL
 \item Concepts: Object Oriented Design, Databases, Vision, Data Structures,
 Algorithms, Operating Systems  % Add graphics
\end{itemize}
\vspace{-3mm}
\section{\scshape Self-taught Skills}
\vspace{-3mm}
I quickly become proficient in new programming languages and technologies through individual study,
and I enjoy challenging myself to learn new skills.
\vspace{2mm}
\begin{itemize}
 \item Languages: {\bfseries Ruby}, \CPP, \CS, \textls{\LaTeX}
 \item Web: Zurb Foundation, Rails, Haml, SASS, PostgreSQL
 \item Experienced Vim user, Ubuntu/Linux, Git/GitHub
 \item Visual Studio, Adobe CS6, Unity3D, Autodesk ECS
\end{itemize}

\vspace{-3mm}
\section{\scshape Projects / Accomplishments}
\vspace{-3mm}

\begin{itemize}
 \item Placed in the top 10 in the 2013 Rocky Mountain Regional ACM International Collegiate Programming Contest.
 \item Developing an automated test generator for Python, working with another section leader remotely. We use GitHub to
 manage and review each other's code, as well as keep track of open issues and feature requests. It produces runnable
 scripts that students and section leaders can use to test and grade programs. I focus on the
 area that does the testing and grading, in addition to the Qt GUI frontend. Our codebase is
 completely unit tested.
%  \item Created a note-taking application that allows users to create accounts,
%  subscribe to boards, and add notes to those boards. In a short period of time my partner and I learned how to
%  use JSP and JDBC to connect to our Oracle database. I designed the front-end using Foundation and various JavaScript plugins.
 \item Created a blog application using PHP, JavaScript, and MySQL. It allows for posts in
 multiple categories, and comments on those posts. In a short period of time I learned how to deal with
 security and keeping data safe, designing/using a database, and understanding AJAX and asynchronous programming.
 \item Built a 2D Tower Defense game in Java, complete with networked two-player, sounds, and animation. Worked on 
 a team of four, using GitHub to manage our code. I developed the majority of the project, focusing on the
 overall design, game logic/mechanics, and visuals.
\end{itemize}


\Hsep

\section{\scshape Employment History}

% \vspace{2mm}
\vspace{-2mm}
\subsection{Section Leader, Teaching Assistant - {\small University of Arizona}}
% \vspace{-2mm}
\begin{adjustwidth}{2em}{0pt}
% {\large \emph{Courses}}

Beginning Python {\small (Head Section Leader)} \hfill January - December 2013

Intro Web Design \hfill August - December 2013

Comparative Programming Languages {\small (Haskell, Prolog, Ruby)} \hfill June - July 2013

SISTA Summer Game Design Workshop \hfill June 2013

\vspace{3mm}
{\large \emph {Responsibilities}}

\hspace{2em}Lead weekly discussion section for 15 - 30 students

\hspace{2em}Respond to student questions via email and office hours

\hspace{2em}Hold open lab hours for any Computer Science student

\hspace{2em}Create/grade assignments and exams, critique lecture material, assist the professor
\end{adjustwidth}

\end{minipage}
\end{document}